Preliminary stuff

### 2022-11-15 code/process.Rmd
fix vars, count NAs

# TODOs
 - will need count of studies excluded for 
 reproducibility / non-exp / missing
 - Fill in ES conversion for non d/SMD/partial eta (and check for correct conversion of those)
 - check & fill on_turk columns

@@

```{r}
d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=2) |> 
  select(target_lastauthor_year, status, academic_year, subfield, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_pvalue, target_ES_type, target_ES_value,
         replication_N, replication_test, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code)

@@

```{r, message=T}
d_corr <- d |> filter(!status %in% c("missing", "non-experiment")) |> 
  mutate(replicated_instructor_code=as.numeric(replicated_instructor_code)) |> #forcibly convert the ?s to NAs
  filter(!is.na(replicated_instructor_code) & !is.na(replicated_report_code))

@@

d_es <-  d |> filter(!status %in% c("missing", "non-experiment")) |> 
  rowwise() |> 
  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))

@@

need to code publication year

```{r}
# needs publication year
d_demo <- d_es 
```

@@

will need to recode mixed designs so they can be binarized

```{r}
d_design <- d_es |> 
  mutate(is_within=case_when(
    within_between=="within" ~ 1,
    within_between=="between" ~ 0),
    log_trials=log(repeated_measure),
    log_sample=log(target_N))|> 
  select(is_within, single_vignette,log_trials, log_sample, replicated_report_code, academic_year)

>>>>

# TODOs
 - Fill in ES conversion for non d/SMD/partial eta (and check for correct conversion of those)

@@

```{r}
d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=2) |> 
  select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_pvalue, target_ES_type, target_ES_value,
         replication_N, replication_test, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code)

# Exclusions

```{r}
d |> group_by(status) |> tally()
```

# How much missing data?

```{r, message=T}
message("total rows")
d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> nrow()

message("number of NAs per column")

d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
pivot_longer(everything()) |> 
  arrange(desc(value)) |> 
  filter(value!=0)

@@

```{r, message=T}
d_corr <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> 
  mutate(replicated_instructor_code=as.numeric(replicated_instructor_code)) |> #forcibly convert the ?s to NAs
  filter(!is.na(replicated_instructor_code) & !is.na(replicated_report_code))

@@

d_es <-  d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> 
  rowwise() |> 
  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))

@@

```{r}
d_demo <- d_es |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year)) |> 
  select(target_year, pub_year, subfield, replicated_report_code, academic_year)

summary(d_demo)
d_demo |> group_by(subfield) |> tally()
```

@@

```{r}
d_design <- d_es |> 
  mutate(is_within=case_when(
    within_between=="within" ~ 1,
    within_between=="mixed" ~ 1,
    within_between=="between" ~ 0),
    log_trials=log(repeated_measure),
    log_sample=log(target_N))|> 
  select(is_within, single_vignette,log_trials, log_sample, replicated_report_code, academic_year)
